---
title: "Simple document"
name: "Trina Hofrenning"
date: "2023-09-12"
output: github_document
---

```{r, echo = FALSE, messge = FALSE}
library(tidyverse)
library(ggplot2)
library(rlang)
library(knitr)
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: Make a plot

This code is borrowed from last lecture- this code creates a dataset for a plot.

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )
```

Next up is a histogram of the `x` variable in `plot_df`

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

  
# Section 4

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r}
#set <-
#data.frame(
#  r_norm = rnorm(500, mean = 1),
#  big_zero = r_norm > 0,
#  abs_val = abs(r_norm)
#)
```

  
  